Manuscript Figures

### 2024-04-03 manuscript_figures.Rmd
manuscript edits

circlize_dendrogram(dend %>% color_branches(k = 2),
                    labels_track_height = NA,
                    dend_track_height = 0.5,
                    labels = TRUE) 
stats 
```

@@

```{r}
infected_vs_healthy_plot %>% 
  mutate(sign = case_when(log2FC < 0 ~ "negative",
                          TRUE ~ "positive")) %>% 
  filter(adj.pvalue <= 0.05) %>% 
  group_by(sign) %>% 
  summarise(n = n())

@@

library(VennDiagram)

venn.diagram(
        x = list(both_sig, faecalis_sig, faecium_sig),
        category.names = c("E.facalis + E.faecium" , "E.faecalis " , "E.faecium"),
        filename = "../Manuscript/02_figures/f2_infection_v_healthy_proteomics/f2a-venn_diagram.svg",
        output=TRUE,

        # Output features
        imagetype="svg" ,
        height = 5 , 
        width = 5 , 
        units = "in",

        # Circles
        lwd = 2,
        lty = 'blank',
        fill = myCol,

        # Numbers
        cex = .6,
        fontface = "bold",
        fontfamily = "sans",

        # Set names
        cat.cex = 0.6,
        cat.fontface = "bold",
        cat.default.pos = "outer",
        cat.pos = c(-27, 27, 135),
        cat.dist = c(0.055, 0.055, 0.085),
        cat.fontfamily = "sans",
        rotation = 1
)

@@

ggsave("02_figures/f2_infection_v_healthy_proteomics/f2d.pdf",f2d,height = 8, width = 8)

>>>>

circlize_dendrogram(dend %>% color_branches(k = 2),
                    labels_track_height = NA,
                    dend_track_height = 0.5,
                    labels = TRUE) 
```

@@

```{r}
infected_vs_healthy = readr::read_csv("01_r_processed_data/Infected_vs_Healthy.csv") %>% 
  left_join(protein_to_gene,by = c("uniprotid"= "ProteinID"))

infected_vs_healthy %>% 
  mutate(sign = case_when(log2FC < 0 ~ "negative",
                          TRUE ~ "positive")) %>% 
  filter(adj.pvalue <= 0.05) %>% 
  group_by(sign) %>% 
  summarise(n = n())

@@

@@

#ggsave("02_figures/f2_infection_v_healthy_proteomics/f2d.pdf",f2d,height = 8, width = 8)
